\section{Introduction}
Creating pencil sketches have a very long history. Throughout time artist have
perfected the art of creating pencil drawings in all thinkable styles, ranging
from completely abstract to stunningly photorealistic. However such skills are
rare, and only well trained artists or passionated hobby artists are able to
actually create pleasing looking images using nothing but the eye, a paper and a
pencil. Today, in a time where cameras can be used to capture a realworld scene
in a matter of seconds, with accurate proportions and colors and no skills, the
need for pencil sketches seem to be gone.  However, photographs do not convey
the same emotions that sketches do. There is a certain timeless flair to pencil
sketches that makes them just nice to look at.

Therefore designing an pencil sketch filter, which produces a pencil sketch from
a regular photograph is an exciting task. The filter described in
\cite{mainPaper} is such a filter, which consists of two stages: sketching the
outlines and drawing the shading. In the sketch stage the filter calculates several
line convolutions and the shading stage solves a huge linear system of
equations. Both tasks are computationally rather expensive and according to the
authors their implementation of the filter takes 2 seconds to run on a
$600\times 600$ image. \autoref{fig:teaser} shows input, intermediate
results and the final result of the filter.

This report presents our efforts to implement the entire filter on the GPU using
Cuda, to gain realtime results. The structure of the report is as follows: The
filter itself is described in \autoref{method}, then in
\autoref{gpu-implementation} we describe our implementation using Cuda.
\autoref{performance} shows our benchmarking results for various input images
and \autoref{future-work} some possible optimizations and applications for our
implementation.
